---
title       : GETTING STARTED ON SLIDIFY
subtitle    : Some basic tips    
author      : Andres Borrero Monge
job         : Data Science almost Specialist
framework   : shower      # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## How to start from zero

1. Install in R the package "devtools"
2. Install via github the slidify package and run its library:
```{r, results ='hide', eval= FALSE}
 install_github('slidify', 'ramnathv')
 library(slidify)
```
3. After setting the working directory, create the folder you will work on:
```{r, results ='hide', eval= FALSE}
 author"second_deck"
```


--- 

## Now tha you have the index.Rmd file

4. Create the basic formatting in the YAML or the index.Rmd
5. Now run the function slidify with this file and open it with your favorite browser:

```{r, results ='hide', eval= FALSE}
 slidify( "index.Rmd")
 browseURL("index.html")
```
5. Try different types of frameworks, as it is the most 
  significant formatting you will see.


--- 

## Now Some Code

Let's see how simple coding works showing results and evaluating it. But without showing the code (echo = FALSE). The code is creating a random normal vector, showing the mean, its standard deviation and its histogram.

```{r, echo=FALSE}
  x <- rnorm(100)
  mean(x)
  sd(x)
 
 
```


---  

## Slide 4

Thank you for taking the time to learn some basics. 
..
Now, take a look at the last slide (5) and see the histogram. 
Each time you refresh it, is a new histogram created? Not yet...
Interactive slidify will be presented in some new presentation.

#PRACTICE IT!

--- 
## Slide 5


```{r, echo=FALSE}
 hist(x)
```

Thank you for taking the time to learn some basics. 

Now, 

#PRACTICE IT!
